---
title: "Test Rt Interactive Visualisation"
author: "Hamish Gibbs"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE}
htmltools::includeHTML("../index.html")
```

#### Note:
map colours currently have nothing to do with r0 plot  
using dummy data for time of infection plot

#### Questions: 
how is 'increasing/decreasing' defined?  
where are case counts and time of infection coming from (this could be a second interactive plot panel) - can you output a csv?  
which r0 dataset to use?  
how to define x axis start in r0 plots?  
How to pull from correct tree on GitHub to get latest data?

#### Possible feature additions (let me know):
addition of time of infections plot (line and bar)  
interactivity for plots (show u90%, l90%, u50%, l50%) in a side panel for each interactive plot
option to interact or serve static .pngs (already made)

#### Issue requests
one output of nowcast with cases column csv
on output of country name (or iso) and 'increasing/decreasing/etc.'
NAs set to 0 in cases column

#### HG To do:
read data from epiforecasts github source  
properly space and zoom map svg within div to center countries (remove large whitespace at bottom)  
map legend  
fix chart x axis label overlap  
put vis components into individual .js files  
r0 plot y axis label  
lines thinner and cleaner  
ensure there are no name conflicts between geo file and rt.csv  
ensure proper spacing of map and chart in place  
test on mobile  
change format of x label to not include weekday names  
